### 2017-02-08 doc/manuscript.Rmd
Included wording on using CV for prediction

While GEE accounts for the longitudinal design of the data, this approach is 
limited in that it cannot analyze the inherent multivariate nature of the 
composition of the TAGFA fraction. To confirm the GEE results in a multivariate 
environment (i.e. all TAGFA analyzed collectively), partial least squares regression (PLS) was
used to identify the patterns of TAGFA composition against insulin sensitivity
and beta-cell function. For a detailed explanation of PLS see the Supplemental
Methods, but briefly, PLS is a technique that extracts latent structures
(clusters) underlying a set of predictor variables conditional on a response
variable(s) (i.e. the outcome variables). These extracted latent structures can
be used to calculated the predicted value of the outcome values, determining how
well TAGFA predict metabolic function by comparing to the measured metabolic function.

>>>>

While GEE accounts for the longitudinal design of the data, this approach is 
limited in that it cannot analyze the inherent multivariate nature of the 
composition of the TAGFA fraction. To confirm the GEE results in a multivariate 
environment (i.e. all TAGFA analyzed collectively), partial least squares regression (PLS) was
used to identify the patterns of TAGFA composition against insulin sensitivity
and beta-cell function. For a detailed explanation of PLS see the Supplemental
Methods, but briefly, PLS is a technique that extracts latent structures
(clusters) underlying a set of predictor variables conditional on a response
variable(s) (i.e. the outcome variables). We determined the predictive strength
of modeling the TAGFA composition on metabolic function by using
cross-validation on the PLS model.
